\bf Classification and Regression on Random Dot Product Graphs

### 2023-11-17 draft.tex
removed large file

\bigskip
\begin{abstract}
The random dot product graph (RDPG) has become a powerful modeling tool
in uncovering latent structures within graphs. In particular, it has
been shown that the RDPG describes a wide range of popular random graph
models with rigid latent structures. More recently, joint modeling of
mutliple random graphs that share common properties or structures across
graphs have been introduced, such as the multilayer RDPG, multiple RPDG,
multilayer stochastic block model, etc. In this work, we use these joint
random graph models in the context of statistical learning, such as
classification and regression, by introducing the multiple latent
structure model, in which the graphs share a common latent structure
with different parameters that correspond to different response
variables. Then we propose various estimation techniques involving
manifold learning to estimate these parameters and in turn predict the
responses, with theorems guaranteeing convergence of the predictions.
Simulations and applications on functional MRI data verify the
performance of these methods.
\end{abstract}

@@

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Draw response variables \(y_1, ..., y_n \iid \Multinomial(1/2, 1/2)\).
\item
  For each \(i = 1, ..., n\), draw
  \(t_i \mid y_i \indep \Betadist(\alpha_{y_i}, \beta_{y_i})\), such
  that

  \begin{itemize}
  \tightlist
  \item
    \(\alpha_1 = 1\)
  \item
    \(\beta_1 = 2\)
  \item
    \(\alpha_2 = 2\)
  \item
    \(\beta_2 = 1\)
  \end{itemize}
\item
  Construct each latent vector as \(x_i = g(t_i)\) and compile them in
  data matrix \(X = \bigl[ x_1 \; \cdots \; x_n \bigr]^\top\).
\item
  Sample graph and its adjacency matrix as \(A \sim \RDPG(X)\).
\end{enumerate}

@@

In this dataset, there are \(N = 516\) graphs (corresponding to
individual subjects), each with \(n = 84\) vertices (corresponding to
brain regions). Analyzing these graphs as RDPGs reveals that the DCBM is
a good candidate for these data (figure \ref{fig:hcp-ase}).

@@

{\centering \includegraphics[width=1\linewidth]{draft_files/figure-latex/hcp-age-regression-degree-1}

\caption{Scatterplot between the subject age (in months) vs. the average degree within (left) and between (right) hemispheres.}\label{fig:hcp-age-regression-degree}
\end{figure}

The ASE suggests a latent structure comprised of two line segments, one
for each hemisphere of the brain, that meet at the origin. One possible
parameter is the angle between the two lines. The estimated angles were
observed to correlate with the subject's age, with wider angles
corresponding to older subjects (figure \ref{fig:hcp-age-regression}). A
linear regression setting aside half of the brain connectivity graphs as
test data achieves an RMSE of \(11.89\) months.

Other plausible statistics from the graphs are the average degrees
within and between hemispheres. When analyzing these as stochastic block
models (SBM) or degree corrected block models (DCBM), these statistics
would roughly correspond to the expected edge weights within and between
communities. Both of these statistics are correlated with the target
value (figure \ref{fig:hcp-age-regression-degree}), but a linear model
using them (i.e., \(age \sim degree_{within} + degree_{between}\))
achieves a higher RMSE (\(12.3\) months) while adding another parameter
to the model. Similarly, the assortativity of each graph with respect to
hemisphere results in a higher RMSE of \(156.5\) when regressed on age.

We also note that this structure is consistent with the DCBM. The
multilayer DCBM was previously studied by \citet{agterberg2022joint}

@@

\begin{longtable}[]{@{}lr@{}}
\caption{Correlation between age and various graph
metrics}\tabularnewline
\toprule\noalign{}
Metric & Correlation \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Metric & Correlation \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Angle between hemispheres & 0.558 \\
Degree within hemisphere & 0.436 \\
Degree between hemispheres & -0.499 \\
Number of triangles in left hemisphere & -0.025 \\
Number of triangles in right hemisphere & 0.002 \\
Assortativity w.r.t. hemisphere & 0.436 \\
Transitivity & -0.261 \\
Modularity w.r.t. hemisphere & 0.434 \\
\end{longtable}

>>>>

\bigskip
\begin{abstract}
The random dot product graph (RDPG) has become a powerful modeling tool
in uncovering latent structures within graphs. In particular, it has
been shown that the RDPG describes a wide range of popular random graph
models with rigid latent structures. More recently, joint modeling of
mutliple random graphs that share common properties or structures across
graphs have been introduced, such as the multilayer RDPG, multiple RPDG,
multilayer stochastic block model, etc. In this work, we use these joint
random graph models in the context of statistical learning, such as
classification and regression, by introducing the multiple latent
structure model, in which the graphs share a common latent structure
with different parameters that correspond to different response
variables. Then we propose various estimation techniques involving
manifold learning to estimate these parameters and in turn predict the
responses, with theorems guaranteeing convergence of the predictions.
Simulations, as well as applications on brain connectivity networks,
verify the performance of our methods.
\end{abstract}

@@

We propose our methodology for classification and regression in three
steps:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Curve-fitting algorithm to recover the LSM curves from the ASEs.
\item
  Quasi-maximum likelihood estimation to recover the parameters of the
  underlying distributions.
\item
  Classification or regression to determine the relationship between the
  parameters and the responses.
\end{enumerate}

\hypertarget{estimation-of-the-lsm-curves}{%
\subsubsection{Estimation of the LSM
Curves}\label{estimation-of-the-lsm-curves}}

For curve-fitting, we will restrict the LSM curves to
non-self-intersecting Bezier polynomials \citep{10.5555/320367}. A
polynomial curve of degree \(R\) in \(\mathbb{R}^d\) is uniquely defined
by a Bezier polynomial within the space of Bezier polynomials of degree
at most \(R\), up to reverse order, although there are infinitely many
Bezier polynomials of degree greater than \(R\) that can describe the
curve \citep{SANCHEZREYES2022102118}. We further restrict the curves to
the case \(p(0) = 0\), i.e., the curve begins at the origin. This is
consistent with well-known models such as the DCBM and PABM when viewed
as LSMs or mixtures of LSMs
\citep{Koo_2022, rubindelanchy2017statistical}, as well as real networks
that can adequately be described as LSMs \citep{athreya2020estimation}.
This constraint also removes the reverse order nonidentifiability. Thus,
if \(R\), the degree of the polynomial, can be determined, and the curve
begins at the origin, a collection of \(n \geq R\) unique vectors on the
curve and not at the origin can determine the unique Bezier polynomial
that describes the curve.

A Bezier polynomial of this form, is defined as \begin{equation}
\label{eq:bezier}
p(t; b_1, ..., b_R) = \sum_{r=1}^R \binom{R}{r} b_r (1-t)^r t^{R-r},
\end{equation} where \(b_r \in \mathbb{R}^d\) are Bezier coefficients
(control points). In the scenario in which an adjacency matrix \(A\)
sampled from an LSM with curve \(p\) that can be described by a Bezier
polynomial, the ASE of \(A\) consists of embedding vectors that lie on
or near a rotation of the curve. Then if embedding vectors
\(x_1, ..., x_n \in \mathbb{R}^d\) are such that
\(x_i = p(t_i) + \epsilon_i\) (for simplicity, redefine \(p\) to be the
rotated version of the original curve), the squared loss function for
the curve fit is of the form \begin{equation}
\label{eq:bezier-loss-full}
L(t_1, ..., t_n; b_1, ..., b_R) = \sum_{i=1}^n \big( x_i - p(t_i; b_1, ..., b_R) \big)^2.
\end{equation}

Letting
\(X = \bigl[ x_1 \; \cdots \; x_n \bigr]^\top \in \mathbb{R}^{n \times p}\),
\(T \in \mathbb{R}^{n \times R}\) such that
\(T_{ir} = \binom{R}{r} (1-t_i)^{R-r} t_i^r\),
\(b = \bigl[b_1 \; \cdots \; b_R\bigr]^\top \in \mathbb{R}^{R \times d}\),
the loss function can be rewritten as \begin{equation}
\label{eq:bezier-loss}
L(T, b) = \|X - T b\|_F^2,
\end{equation} where \(\|\cdot\|_F\) is the Frobenius norm. Then if
\(t_1, ..., t_n\) are known, the solution to the least squares best fit
Bezier coefficients is given by the ordinary least squares estimate,
\begin{equation}
\label{eq:bezier-ols}
\hat{b} = (T^\top T)^{-1} T^\top X.
\end{equation}

On the other hand, if the coefficients are known but the timepoints
\(t_1, ..., t_n\) are not, this turns into \(n\) individual minimization
problems for polynomials of degree \(2 R\). More precisely,
\(L(t_1, ..., t_n; b_1, ..., b_R) = \sum_{i=1}^n L(t_i; b_1, ..., b_R)\)
where \begin{equation}
\label{eq:bezier-ls}
L(t_i; b_1, ..., b_R) = x_i - \sum_r \binom{R}{r} b_r (1-t_i)^{R-r} t_i^r. 
\end{equation} To solve, we find the at most \(2 R - 1\) roots of its
derivative, \begin{equation}
\label{eq:dbezier}
\dot{L}(t_i; b_1, ..., b_R) = \bigg(\sum_{r=1}^R \binom{R}{r} (-1)^r c_r t_i^r \bigg) \bigg(\sum_{r=0}^{R-1} \binom{R-1}{r} (-1)^r c_{r+1} t_i^r \bigg) = 0,
\end{equation} where \(c_r = \sum_{s=1}^r (-1)^{r-s} \binom{r}{s} b_s\).
Since each \(t_i\) can be solved separately, this method is highly
parallelizable.

For initialization, the ordering of \(t_1, ..., t_n\) is determined via
a one-dimensional Isomap embedding \citep{Tenenbaum2000-ff}.

Combining equation \ref{eq:bezier-ols} with the solutions to equation
\ref{eq:dbezier} for each \(i = 1, ..., n\) provides an alternating
coordinate descent algorithm, as outlined in algorithm
\ref{alg:bezier-fit}.

\begin{algorithm}[h]
\label{alg:bezier-fit}
\DontPrintSemicolon
\SetAlgoLined
\setstretch{1.1}
\KwData{Adjacency matrix $A$, embedding dimension $d$, polynomial degree $R$, Isomap neighborhood parameter $\lambda$, stopping criterion $\epsilon$.}
\KwResult{Bezier coefficients $\hat{b}$, timepoint values $\hat{t}_1, ..., \hat{t}_n$.}
Compute $\hat{X} \in \mathbb{R}^{n \times d}$, the ASE of $A$.\;
Initialize timepoints $\hat{t}_1, ..., \hat{t}_n$, first via a one-dimensional Isomap embedding of $\hat{X}$ using neighborhood parameter $\lambda$, then by normalizing the embedding to $[0, 1]$.\;
\Repeat {the change in equation \ref{eq:bezier-ls} is less than $\epsilon$.} {
  Fit $\hat{b}$ by equation \ref{eq:bezier-ols}.\;
  \For {$i = 1, ..., n$} {
    Fit $\hat{t}_i$ by equation by finding the roots of equation \ref{eq:dbezier} and choosing the roots that minimizes equation \ref{eq:bezier-ls}.\;
  }
}
\caption{Procedure for estimating an LSM curve as a Bezier polynomial from an adjacency matrix.}
\end{algorithm}

In the case of a mixture of LSMs (as in remark \ref{rem:lsm-mixture}),
algorithm \ref{alg:bezier-fit} is modified by fitting Bezier polynomials
for each vertex label (if the labels are known) or by estimating the
labels via an alternating coordinate descent algorithm outlined in
algorithm \ref{alg:bezier-fit-mixture}.

\begin{algorithm}[H]
\label{alg:bezier-fit-mixture}
\DontPrintSemicolon
\SetAlgoLined
\setstretch{1.1}
\KwData{Adjacency matrix $A$, embedding dimension $d$, polynomial degree $R$, number of latent structures $K$, Isomap neighborhood parameter $\lambda$, stopping criterion $\epsilon$.}
\KwResult{Bezier coefficients $\hat{b}$, timepoint values $\hat{t}_1, ..., \hat{t}_n$, curve memberships $\hat{z}_1, ..., \hat{z}_n$.}
Compute $\hat{X} \in \mathbb{R}^{n \times d}$, the ASE of $A$.\;
Initialize $\hat{z}_1, ..., \hat{z}_n \in \{1, ..., K\}$, the membership of each vertex to each latent curve.\;
\For {$k = 1, ..., K$} {
  Subset the rows of $\hat{X}$ by $z_i = k$ to obtain $\hat{x}_{k_1}, ..., \hat{x}_{k_{n_k}}$, where $n_k$ is the number of vertices with label $k$.\;
  Initialize timepoints $\hat{t}_{k_1}, ..., \hat{t}_{k_{n_k}}$, first via a one-dimensional Isomap embedding of $\hat{x}_{k_1}, ..., \hat{x}_{k_{n_k}}$ using neighborhood parameter $\lambda$, then by normalizing the embedding to $[0, 1]$.\;
}
\Repeat {the change in equation \ref{eq:bezier-ls} is less than $\epsilon$.} {
  \For {$k = 1, ..., K$} {
    Fit $\hat{b}^{(k)}$ by equation \ref{eq:bezier-ols}, using the row subsets of $T$ and $X$ such that $z_i = k$.\;
    \For {$i = 1, ..., n_k$} {
      Fit $\hat{t}_{k_i}$ by equation by finding the roots of equation \ref{eq:dbezier} and choosing the roots that minimizes equation \ref{eq:bezier-ls}.\;
    }
  }
  \For {$k = 1, ..., n$} {
    Reassign $z_i$ based on the latent curve closest to $\hat{x}_i$. 
  }
}
\caption{Procedure for estimating multiple LSM curves as a Bezier polynomial from an adjacency matrix.}
\end{algorithm}

\begin{lemma}[Recovery of LSM curves in noiseless case]
\label{lem:lsm-noiseless}
Suppose $t_1, ..., t_n \iid F_\theta$ such that $F_\theta$ has probability density function $f_\theta(t)$ that is absolutely continuous on support $[0, 1]$ and $\min_t f_\theta(t) > 0$ $\forall t \in [0, 1]$. 
Let each $x_i = p(t_i)$ such that $p: [0, 1] \to \mathbb{R}^d$ is a non-self-intersecting Bezier polynomial of degree $R$ that begins at the origin with unknown coefficients $b_1, ..., b_R$. 
Then there exists a sequence of Isomap neighborhood parameters $\lambda_n \to 0$ such that as $n \to \infty$, algorithm \ref{alg:bezier-fit}, $L(t_1, ..., t_n; b_1, ..., b_R) \stackrel{p}{\to} 0$.
\end{lemma}

\begin{proof}
Let $z_1, ..., z_n$ be the one-dimensional Isomap embedding of $x_1, ..., x_n$ using neighborhood parameter $\lambda_n$, and let $l_{ij}$ be the arc length along the curve defined by $p$ between $x_i$ and $x_j$. 
Then by theorem 5 of \citet{acharyya2023}, $|z_i - z_j| - l_{ij} \stackrel{p}{\to} 0$ $\forall i, j \in \{1, ...,n\}$. 
Let $z_{\min} = \min_i z_i$ and $z_{\max} = \max_i z_i$, and initialize each $\hat{t}_i = (z_i - z_{\min}) / (z_{\max} - z_{\min})$. 
\end{proof}

\begin{theorem}[Recovery of timepoints of the LSM]
Suppose $A \sim \LSM(p, F_\theta)$ such that $p : [0, 1] \to \mathbb{R}^d$ is a bezier polynomial of degree $R$ and $F_\theta$ is a probability distribution with probability density function $f_\theta(t)$ that is absolutely continuous on support $[0, 1]$ and $\min_t f_\theta(t) > 0$ $\forall t \in [0, 1]$. 
Let $\hat{X}$ be the ASE of $A$ with embedding vectors $\hat{x}_1, ..., \hat{x}_n \in \mathbb{R}^d$. 
Let $\hat{t}_1, ..., \hat{t}_n$ be the timepoint estimates outputted by algorithm \ref{alg:bezier-fit}. 
Then there exists a sequence of Isomap parameters $\lambda_n \to 0$ such that as $n \to \infty$, $|t_i - \hat{t}_i| \stackrel{p}{\to} 0$ for each $i, j \in \{1, ..., n\}$. 
\end{theorem}

\hypertarget{recovery-of-the-underlying-distributions}{%
\subsubsection{Recovery of the Underlying
Distributions}\label{recovery-of-the-underlying-distributions}}

\begin{algorithm}[H]
\label{alg:bezier-param-fit}
\DontPrintSemicolon
\SetAlgoLined
\setstretch{1.1}
\KwData{Adjacency matrix $A$, embedding dimension $d$, probability distribution family $F$, polynomial degree $R$, Isomap neighborhood parameter $\lambda$, stopping criterion $\epsilon$.}
\KwResult{Bezier coefficients $\hat{b}$, timepoint values $\hat{t}_1, ..., \hat{t}_n$.}
Compute $\hat{X} \in \mathbb{R}^{n \times d}$, the $d$-dimensional ASE of $A$.\;
Initialize timepoints $\hat{t}_1, ..., \hat{t}_n$, first via a one-dimensional Isomap embedding of $\hat{X}$ using neighborhood parameter $\lambda$, then by normalizing the embedding to $[0, 1]$.\;
\Repeat {the change in equation \ref{eq:bezier-ls} is less than $\epsilon$.} {
  Fit $\hat{b}$ by equation \ref{eq:bezier-ols}.\;
  \For {$i = 1, ..., n$} {
    Fit $\hat{t}_i$ by equation by finding the roots of equation \ref{eq:dbezier} and choosing the roots that minimizes equation \ref{eq:bezier-ls}.\;
  }
}
Estimate $\hat{\theta}$ from $\hat{t}_1, ..., \hat{t}_n$ via maximum likelihood estimation.\; 
\caption{Procedure for estimating the underlying distribution of a Bezier LSM curve from an adjacency matrix.}
\end{algorithm}

\begin{theorem}[Consistency of algorithm \ref{alg:bezier-param-fit}]
\end{theorem}

\hypertarget{classification-and-regression}{%
\subsubsection{Classification and
Regression}\label{classification-and-regression}}

\begin{algorithm}[H]
\label{alg:mlsm-fit}
\DontPrintSemicolon
\SetAlgoLined
\setstretch{1.1}
\KwData{Adjacency matrices $A^{(1)}, ..., A^{(L)}$, response variables $y_1, ..., y_L$, embedding dimension $d$, probability distribution family $F$, polynomial degree $R$, Isomap neighborhood parameters $\lambda_1, ..., \lambda_L$, stopping criterion $\epsilon$.}
\KwResult{Bezier coefficients $\hat{b}$, timepoint values $\hat{t}_1, ..., \hat{t}_n$.}
\For {$\ell = \{1, ..., L\}$} {
  Compute $\hat{X}^{(\ell)} \in \mathbb{R}^{n_\ell \times d}$, the $d$-dimensional ASE of $A^{(\ell)} \in \mathbb{R}^{n_\ell \times n_\ell}$.\;
  Initialize timepoints $\hat{t}_1, ..., \hat{t}_{n_\ell}$, first via a one-dimensional Isomap embedding of $\hat{X}^{(\ell)}$ using neighborhood parameter $\lambda_\ell$, then by normalizing the embedding to $[0, 1]$.\;
  \Repeat {the change in equation \ref{eq:bezier-ls} is less than $\epsilon$.} {
    Fit $\hat{b}$ by equation \ref{eq:bezier-ols}.\;
    \For {$i = 1, ..., {n_\ell}$} {
      Fit $\hat{t}_i$ by equation by finding the roots of equation \ref{eq:dbezier} and choosing the roots that minimizes equation \ref{eq:bezier-ls}.\;
    }
  }
  Estimate $\hat{\theta}_\ell$ from $\hat{t}_1, ..., \hat{t}_{n_\ell}$ via maximum likelihood estimation.\;
}
Fit a model for predicting $y_1, ..., y_L$ using the estimated parameters $\theta_1, ..., \theta_L$ (e.g., via linear regression).\;
\caption{Procedure for fitting a classification or regression model for an MLSM.}
\end{algorithm}

\begin{theorem}
\end{theorem}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Draw response variables \(y_1, ..., y_n \iid \Multinomial(1/2, 1/2)\).
\item
  For each \(i = 1, ..., n\), draw
  \(t_i \mid y_i \indep \Betadist(\alpha_{y_i}, \beta_{y_i})\), such
  that \(\alpha_1 = 1\), \(\beta_1 = 2\), \(\alpha_2 = 2\), and
  \(\beta_2 = 1\).
\item
  Construct each latent vector as \(x_i = g(t_i)\) and compile them in
  data matrix \(X = \bigl[ x_1 \; \cdots \; x_n \bigr]^\top\).
\item
  Sample graph and its adjacency matrix as \(A \sim \RDPG(X)\).
\end{enumerate}

@@

In this dataset, there are \(L = 516\) graphs (corresponding to
individual subjects), each with \(n_\ell = n = 84\) vertices
(corresponding to brain regions). Analyzing these graphs as RDPGs
reveals that the DCBM is a good candidate for these data (figure
\ref{fig:hcp-ase}).

@@

The ASE suggests a latent structure comprised of two Bezier curves of
degree 1 (i.e., lines), one for each hemisphere of the brain, that meet
at the origin. One possible parameter when analyzing these data as a
MLSM is the angle between the two lines. The estimated angles were
observed to correlate with the subject's age, with wider angles
corresponding to older subjects (figure \ref{fig:hcp-age-regression}). A
linear regression setting aside half of the brain connectivity graphs as
test data achieves an RMSE of \(11.889\) months.

To compare this parameter as a covariate for age against other network
statistics, we analyzed these data as a multilayer DCBM, first studied
by \citep{agterberg2022joint}, who proposed the degree corrected
multiple adjacency spectral embedding (DC-MASE) algorithm. Since these
graphs come with hemisphere labels, we did not apply DC-MASE for
community detection but instead used the estimators for the three edge
connectivity parameters, \(B_{LL}\), \(B_{RR}\), and \(B_{LR}\). A
linear model trained on these parameter estimates achieves a higher RMSE
of \(12.889\) months, despite using three covariates instead of one. In
addition, since the angles between the latent structures under the MLSM
depend primarily on the shape of the latent structures rather than the
exact community memberships, it does not depend on recovery of the
original community labels. Ultimately, these two methods are estimators
for transformations of the same parameters, and while we cannot
determine how close these estimates are on the ``true'' edge
connectivity parameters since they are unknown, we observe that the MLSM
estimate is a better linear predictor than the rest.

Other graph statistics were extracted for each brain network, and their
correlations to age are reported in table \ref{tab:cor-comparison}. Note
that aside from the angle between the latent structures under the MLSM
model, these statistics assume that it is known which vertex belongs to
which hemisphere.

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.5915}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1690}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2394}}@{}}
\caption{Correlation between age and various graph
metrics}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Metric
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Correlation
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
95\% conf. int.
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Metric
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Correlation
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
95\% conf. int.
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Angle between hemispheres & 0.558 & (0.496, 0.615) \\
Edge connectivity within left hemisphere & 0.241 & (0.158, 0.321) \\
Edge connectivity within right hemisphere & 0.243 & (0.16, 0.322) \\
Edge connectivity between hemispheres & -0.436 & (-0.503, -0.363) \\
Degree within hemisphere & 0.436 & (0.363, 0.503) \\
Degree between hemispheres & -0.499 & (-0.561, -0.431) \\
Number of triangles in left hemisphere & -0.025 & (-0.111, 0.062) \\
Number of triangles in right hemisphere & 0.002 & (-0.084, 0.088) \\
Assortativity w.r.t. hemisphere & 0.436 & (0.363, 0.503) \\
Modularity w.r.t. hemisphere & 0.434 & (0.362, 0.502) \\
\end{longtable}
